---
title: "Aisha"
author: "Aisha"
date: "November 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sumbission 1

```{r}
library(tidyverse)

credits <- read.csv('tmdb_5000_credits.csv')
str(credits)

movies <- read.csv('tmdb_5000_movies.csv')
str(movies)
```

```{r}
credits1 <- credits %>% separate(cast, into = c('cast1','cast2','cast3','cast4','cast5'), sep = '\\}, \\{')
credits1$cast1 %>% head()

sub("(?:\\[\\{)?\"cast_id\": \\d+, \"character\": \"\\w+(?:..)*(?: \\w+)*\", \"credit_id\": \"\\w+\", \"gender\": \\d, \"id\": \\d+, \"name\": \"(\\w+ ?\\w+?)\", \"order\": \\d", "\\1", credits1$cast2) %>% head()

credits1$cast1 <- sub("(?:\\[\\{)?\"cast_id\": \\d+, \"character\": \"\\w+(?:..)*(?: \\w+)*\", \"credit_id\": \"\\w+\", \"gender\": \\d, \"id\": \\d+, \"name\": \"(\\w+ ?\\w+?)\", \"order\": \\d", "\\1", credits1$cast1)
credits1$cast2 <- sub("(?:\\[\\{)?\"cast_id\": \\d+, \"character\": \"\\w+(?:..)*(?: \\w+)*\", \"credit_id\": \"\\w+\", \"gender\": \\d, \"id\": \\d+, \"name\": \"(\\w+ ?\\w+?)\", \"order\": \\d", "\\1", credits1$cast2)
credits1$cast3 <- sub("(?:\\[\\{)?\"cast_id\": \\d+, \"character\": \"\\w+(?:..)*(?: \\w+)*\", \"credit_id\": \"\\w+\", \"gender\": \\d, \"id\": \\d+, \"name\": \"(\\w+ ?\\w+?)\", \"order\": \\d", "\\1", credits1$cast3)
credits1$cast4 <- sub("(?:\\[\\{)?\"cast_id\": \\d+, \"character\": \"\\w+(?:..)*(?: \\w+)*\", \"credit_id\": \"\\w+\", \"gender\": \\d, \"id\": \\d+, \"name\": \"(\\w+ ?\\w+?)\", \"order\": \\d", "\\1", credits1$cast4)
credits1$cast5 <- sub("(?:\\[\\{)?\"cast_id\": \\d+, \"character\": \"\\w+(?:..)*(?: \\w+)*\", \"credit_id\": \"\\w+\", \"gender\": \\d, \"id\": \\d+, \"name\": \"(\\w+ ?\\w+?)\", \"order\": \\d", "\\1", credits1$cast5)

credits %>% select(cast) %>% head()
```

Separate Genre into `genre1`, `genre2`, `genre3`

```{r}
movies1 <- movies %>% separate(genres, into = c('genre1','genre2','genre3'), sep = '\\}, \\{')

movies1$genre1 <- sub("(\\[\\{)?\"id\": \\d+, \"name\": \"(\\w+ ?\\w+?)\"(\\}\\])?", '\\2', movies1$genre1)
movies1$genre2 <- sub("(\\[\\{)?\"id\": \\d+, \"name\": \"(\\w+ ?\\w+?)\"(\\}\\])?", '\\2', movies1$genre2)
movies1$genre3 <- sub("(\\[\\{)?\"id\": \\d+, \"name\": \"(\\w+ ?\\w+?)\"(\\}\\])?", '\\2', movies1$genre3)
```



1. The names of all team members that worked on the document.
2. An overview of the data set you are working with for the final project
3. A discussion of cleaning steps that are necessary to get the data into the right shape

![The Godfather]<https://m.media-amazon.com/images/M/MV5BM2MyNjYxNmUtYTAwNi00MTYxLWJmNWYtYzZlODY3ZTk3OTFlXkEyXkFqcGdeQXVyNzkwMjQ5NzM@._V1_SY1000_CR0,0,704,1000_AL_.jpg>

1. Lynn Hyuang, Prateek Oberoi, Aisha Washington
2. We are working with TMDB_5000_Movie Dataset from The Movie Database.  There are two tables: One with information on various aspects of movies such as an identifier number for each movie, the title, the cast, and the crew; the second with information on the budget, genres,revenue, and other items specific to the movie's audience facing perception.
3. Selecting variables of interest: We can use select statements in order to work with only the factors that we're interested in.    
   Separating genres and keywords from filler text: Since the genre and keyword categories are often different for each observation, we can use regular expressions in order to create a genereal formula for what needs to be removed, select variables of interest
   
